\textbf{NBA Party}

### 2017-07-15 cardinal_analytx_presentation/nightlife_and_sports.tex
Minor changes. Added a footnote.

\begin{frame}
  \frametitle{Previous research - NBA player shooting average}
  \begin{block}{Empirical evidence: players party to the detriment of the game.}
  NBA Players under-perform proportion of shots made on Sundays.\footnote{Chase, ('15).}
  \end{block}
    \begin{itemize}       
    \item 1,092 of 2,035 NBA players who took $\geq 1$ shot on Sundays       under-perform 
      relative to their own career-long average;\footnote{Analysis limited to all players who entered the league after 1974.} $p=0.001$.
    \end{itemize}
    \begin{block}{Problems}       \begin{itemize}           \item Effect size is not considered.
          \item Density of support is questionable.\footnote{What if we miss the only shot we took on Sunday, is that relevant?}            \end{itemize}     \end{block}
\end{frame}

@@

\begin{frame}   \frametitle{Data: 2010-11 through 2016-17}
  \begin{block}{NBA Data}     \begin{itemize}       \item Total of $82 \times 30 / 2 = 1,230$ games per season.
      % \item Missing the first couple months of 2010-11 season.
      \item Total of 7,829 games in our dataset.     \end{itemize}
  \end{block} 
  \begin{block}{MLB Data}     \begin{itemize}       \item Total of $162 \times 30 / 2 = 2,430$ games per season.
      % \item We have on average 2,100 games per season.
      \item Total of 12,709 games in our dataset.     \end{itemize}   \end{block}
  \begin{block}{BLS Data}
    \begin{itemize}       \item \# establishments by MSA-quarter-year.
      \item Excludes Toronto from our analysis.     \end{itemize}   \end{block}
  \begin{block}{ESPN Data}     \begin{itemize}       \item Describes \# shots taken for each player in each game.
      \item 85\% of our season-teams have no more than 3 missing games.     \end{itemize}   \end{block} \end{frame}

@@

\begin{frame}   \frametitle{Feature creation}
  We add features which describe
  \vspace{12pt}  
  \begin{itemize}     
    \item Number of days since the last game (i.e. rest-time),
    \item Lagged changes in possession,\footnote{A crude measure of fatigue incurred from last game.}
    \item Lagged game location, and
    \item Travel Distance.   
  \end{itemize}
  \vspace{12pt}We seek to construct a model which accounts for travel-fatigue and jet-lag.
  For this, we need a little bit more. \end{frame}

>>>>

\begin{frame}
  \frametitle{Previous research - NBA player shooting average}
  \begin{block}{Empirical evidence: players party to the detriment of the game.}
  NBA Players under-perform proportion of shots made on Sundays.\footnote{Chase, ('15).}
  \end{block}
    \begin{itemize}       
    \item 1,092 of 2,035 NBA players who took $\geq 1$ shot on Sundays       under-perform 
      relative to their own career-long average;\footnote{Analysis limited to all players who entered the league after 1974.} $p=0.001$.
    \end{itemize}
    \begin{block}{Problems}       \begin{itemize}           \item Effect size is not considered.\footnote{What if a player scores 50\% of shots taken, but only 49\% on Sundays?}
          \item Density of support is questionable.\footnote{What if we miss the only shot we took on Sunday, is that relevant?}            \end{itemize}     \end{block}
\end{frame}

@@

\begin{frame}   \frametitle{Data: 2010-11 through 2016-17}
  \begin{block}{NBA Data}     \begin{itemize}       \item Total of $82 \times 30 / 2 = 1,230$ games per season.
      % \item Missing the first couple months of 2010-11 season.
      \item Total of 7,829 games in our dataset.     \end{itemize}
  \end{block} 
  \begin{block}{MLB Data}     \begin{itemize}       \item Total of $162 \times 30 / 2 = 2,430$ games per season.
      % \item We have on average 2,100 games per season.
      \item Total of 12,709 games in our dataset.     \end{itemize}   \end{block}
  \begin{block}{BLS Data}
    \begin{itemize}       \item \# establishments by MSA-quarter-year.
      \item Excludes Toronto from our analysis.     \end{itemize}   \end{block}
  \begin{block}{ESPN Data (NBA)}     \begin{itemize}       \item Describes \# shots taken for each player in each game.
      \item 85\% of our season-teams have no more than 3 missing games.     \end{itemize}   \end{block} \end{frame}

@@

\begin{frame}   \frametitle{Feature creation}
  We add features which describe
  \vspace{12pt}  
  \begin{itemize}     
    \item Number of days since the last game (i.e. rest-time),\footnote{Note: if we are missing games in our dataset, this metric is affected.}
    \item Lagged changes in possession,\footnote{A crude measure of fatigue incurred from last game.}
    \item Lagged game location, and
    \item Travel Distance.   
  \end{itemize}
  \vspace{12pt}We seek to construct a model which accounts for travel-fatigue and jet-lag.
  For this, we need a little bit more. \end{frame}
